### 2014-09-03 tex/proofs.tex
Fixed some typos in the math the kept the paper from building.

We begin by considering the Field Access rule. Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule. The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$. Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ... , s_n$. We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states. First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$. If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$. 
Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location. In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$. The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnf{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$. The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations. Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$. The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$. The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$. Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$. Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.

@@

Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
$$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
$$\forall a \in \cfgnt{L}_0^\rightarrow ( h(a) = a )$$ 
Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$. Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rigtharrow_h s_0 ) ) $ must evaluate to true. Thus, any state in the feasible set must be represented by $s_0$: :
$$s_0 \in \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
$$ \{s_0\} = \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) )$$
Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$. Since every feasible state sequence starts with an initial state, we now know that:
 $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$

>>>>

We begin by considering the Field Access rule. Suppose $s_s$ has the form $\lp \cfgnt{L}_s\ \cfgnt{R}_{s}\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. In this case, the relationship between $s_s$ and $s_s^\prime$ is described by the Field Access rule. The Field Access rule uses the Summarize rule to describe the relation between $\cfgnt{L}_{s}$ and $\cfgnt{L}_{s^\prime}$. Because the summarize rule is essentially a fixed-point computation, we can reason about it as a machine that produces a sequence of intermediate states $s_1, s_2, ... , s_n$. We will use an inductive argument to show that the mutual exclusion property holds for any of those intermediate states. First, let state $s_\alpha$ be any state for which the property in Theorem~\ref{thm:mutex} holds, and let $s_\beta$ be the intermediate state where $s_\alpha \rightarrow_S s_\beta$. If all fields are initialized, then $s_\alpha$ and $s_\beta$ are identical, so the mutually exclusive property holds for $s_\beta$. 
Otherwise, there must be some location $\cfgnt{l}_{un} \in \cfgnt{L}_\alpha(r)$ for which field f contains a reference $r_a$ that could feasibly point to the uninitialized location. In this case, a new reference is created and a single entry is added to $\cfgnt{L}_\beta$. The elements of the set $\theta_{all} = \cfgnt{L}_\beta(\cfgnt{R}_\beta(\cfgnt{l}_{un},\cfgnt{f}))$ can be divided into four distinct subsets, $\theta_{cur}$, $\theta_{null}$, $\theta_{new}$, and $\theta_{alias}$. The set $\theta_{cur}$ contains the pairs containing locations from the reference $r_a$, $\theta_{null}$ contains the pair with the null location, $\theta_{new}$ contains a pair with a new location, and $\theta_{alias}$ contains pairs representing alias locations. Any two constraints in $\theta_{cur}$ are guaranteed to be pairwise mutually exclusive because of the inductive hypothesis, and any single constraint is guaranteed to be pairwise mutually exclusive with any constraint in $\theta_{null}$, $\theta_{new}$, or $\theta_{alias}$ because constraints in $\theta_{cur}$ contain the conjunct $\neg \phi$, while constraints in the other three sets are conjoined with $\phi$. The set $\theta_{null}$ contains only one element, which in turn contains the constraint $r_f = r_{null}$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{new}$, or $\theta_{alias}$ because constraints in those sets contain the conjunct $r_f \neq r_{null}$. The set $\theta_{new}$ contains one element, which in turn contains the constraint containing the conjunct $ \wedge_{\lp \cfgnt{r}^\prime_a,\ \phi^\prime_a,\ l^\prime_a\rp  \in \rho} \cfgnt{r}_f \ne \cfgnt{r}^\prime_a$, which is guaranteed to be mutually exclusive with any constraint in $\theta_{alias}$, because each constraint in that set contains the conjunct $r_f = r_a$ for some $(r_a\ \phi_a\ l_a)\in \rho$. Any two elements of the set $\theta_{alias}$ are guaranteed to pairwise mutually exclusive because for each constraint that contains the conjunct $r_f = r_a$, every other constraint contains the conjunct $r_f \ne r_a$. Thus, all constraints from all pairs in $\theta{all}$ are guaranteed to be mutually exclusive, and the property from Theorem~\ref{thm:mutex} holds for intermediate state $s_\beta$.

@@

Base case: For any initial state $s_0$, the feasible state set contains a single element, $\{s_0\}$:
$$\mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0)) = \{s_0\}$$
We can define a homomorphism from $s_0$ to $s_0$ using the identity function: 
$$\forall a \in \cfgnt{L}_0^\rightarrow ( h(a) = a )$$ 
Because the only constraints in the heap are $\mathit{true}$, the heap constraint evaluates to $\mathit{true}$. Since $phi_0$ also evaluates to $\mathit{true}$, the expression $\mathbb{S}(\phi_0 \wedge \mathbb{HC}(s_0 \rightarrow_h s_0 ) ) $ must evaluate to true. Thus, any state in the feasible set must be represented by $s_0$: :
$$s_0 \in \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) ) \Rightarrow s_0 \sqsubset s_0$$
Furthermore, since every reference points to a single place, there is only one possible represented heap. Thus:
$$ \{s_0\} = \mathbb{FS}(\rightarrow_\ell,s_0, (\eta_0\ e_0\ k_0) )$$
Since $s_0$ is the only represented heap, and since we know $s_0$ is in the feasible set, 
$$s_0 \sqsubset s_0 \Leftrightarrow s_0 \in \{s_0\}$$
We have now shown that $s_0 \cong \mathbb{FS}(\rightarrow_\ell, (s_0), \mathbb{CF}(s_0))$ for an arbitrary initial state $s_0$. Since every feasible state sequence starts with an initial state, we now know that:
 $$\mathit{last}(\Pi_1^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_1^s), \mathbb{CF}(\Pi_1^s) ) $$
